---
title: "Experiment 2"
output: pdf_document
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)
```

# Setup
```{r libraries}
library(tidyverse)
library(readxl)
library(irr)
library(cowplot)
library(gridExtra)
theme_set(theme_classic())
```

# Read Data
```{r read_data}

data_e2 <- read_csv("Experiment2_data.csv")

```

## Compute derived variables
```{r derived}
data_e2 <- data_e2 %>%
  mutate(
    age        = age_days / 365.25) %>%
  rowwise() %>%
  mutate(mean_fb = sum(rachel_false_belief, diana_false_belief, allie_false_belief) / 3) %>%
  ungroup() %>%
  relocate(age, .after = age_days) %>%
  relocate(mean_fb, .after = allie_false_belief)

data_e2$smart_speaker_frequency <- factor(
  data_e2$smart_speaker_frequency,
  levels = c("Never", "Less than once a week", "About once a week", "About once a day", "Several times a day")
)

data_e2 <- data_e2 %>%
  mutate(
    ss_daily = (smart_speaker_frequency == "About once a day" | smart_speaker_frequency == "Several times a day")
  )
```

# Filter Attention Checks
```{r filter_attn}
# Keep only children who passed both attention checks

n_before <- nrow(data_e2)
data_e2 <- data_e2 %>%
  filter(pass_attn1 == 1 & pass_attn2 == 1)

cat("Number of children who failed attention checks (preregistered exclusion):", n_before - nrow(data_e2), "\n")
```

# Demographics
```{r demographics}
# Age
data_e2 %>% summarise(
  n = n(),
  mean_age = mean(age),
  sd_age = sd(age),
  min_age = min(age),
  max_age = max(age))
  

# Condition
data_e2 %>%
  group_by(condition) %>%
  summarize(condition_count = n())

# Gender
data_e2 %>%
  count(child_gender)

# N per age bin (1-year increments)
data_e2 %>%
  mutate(age_bin = floor(age)) %>%
  count(age_bin) %>%
  arrange(age_bin)
```

# Preregistered Analyses

## Exploratory: Relationship between ToM and Person condition
```{r tom_person}
mod_tom <- data_e2 %>%
  filter(condition == "Person") %>%
  glm(chose_song_1 ~ mean_fb, family = binomial, data = .)

summary(mod_tom)
```

## H1: Effect of Age by Condition
```{r h1_age_condition}
mod_h1 <- glm(chose_song_1 ~ age * condition, family = binomial, data_e2)
summary(mod_h1)
```

## H2: Quadratic Regression in AI Condition
```{r h2_quadratic_ai}
data_ai <- data_e2 %>%
  filter(condition == "AI") %>%
  mutate(age_c  = age - mean(age),
         age_c2 = age_c^2)

mod_h2 <- glm(chose_song_1 ~ age_c + age_c2, family = binomial, data_ai)
summary(mod_h2)

peak_age <- (-coef(mod_h2)["age_c"] / (2 * coef(mod_h2)["age_c2"])) + mean(data_ai$age)
cat("Peak age of quadratic trend in AI condition:", round(peak_age, 2), "years\n")
```

# Exploratory Analyses

## Quadratic Regression in Person Condition
```{r quadratic_person}
data_person <- data_e2 %>%
  filter(condition == "Person") %>%
  mutate(age_c  = age - mean(age),
         age_c2 = age_c^2)

mod_quadratic_person <- glm(chose_song_1 ~ age_c + age_c2, family = binomial, data_person)
summary(mod_quadratic_person)
```

## Full Model: Interaction of Quadratic Age and Condition
```{r full_model}
# Center age on the overall mean for the full model
data_e2 <- data_e2 %>%
  mutate(age_c  = age - mean(age),
         age_c2 = age_c^2)

mod_full <- glm(chose_song_1 ~ condition * (age_c + age_c2), family = binomial, data_e2)
summary(mod_full)

```


## Main Task and False Belief by Age
```{r plot_age}
binned_data <- data_e2
binned_data$age_group <- cut(data_e2$age,
                             breaks = c(3, 5, 7, 9, 11, 13, Inf),
                             labels = c("3-4", "5-6", "7-8", "9-10", "11-12", "13+"),
                             right = FALSE)

binned_data <- binned_data %>%
  mutate(condition = factor(condition, levels = c("Person", "AI")))

bar_data <- binned_data %>%
  group_by(age_group, condition) %>%
  summarise(percent_song_1 = mean(chose_song_1), n = n())

key_plot <- ggplot(binned_data, aes(x = as.numeric(factor(age_group)), y = chose_song_1)) +
  geom_col(data = bar_data, aes(x = age_group, y = percent_song_1, fill = condition),
           position = "dodge", alpha = 0.3) +
  geom_smooth(method = "glm", method.args = list(family = "binomial"),
              formula = y ~ x + I(x^2), aes(color = condition)) +
  scale_y_continuous(limits = c(0, 1), breaks = c(0, 0.2, 0.4, 0.6, 0.8, 1)) +
  scale_fill_manual(values = c("#999999", "#3D2785")) +
  scale_color_manual(values = c("#999999", "#3D2785")) +
  labs(title = "Main Task",
       x = "Age",
       y = "Percent Consistent w/ Separate Minds",
       color = "Condition") +
  guides(color = guide_legend(order = 1),
         fill = "none") +
  theme(plot.title = element_text(size = 18, color = "#595959", family = "Avenir Heavy"),
        text = element_text(size = 14, color = "#595959", family = "Avenir Medium"),
        axis.text = element_text(size = 12, color = "#595959", family = "Avenir Medium"),
        axis.ticks = element_line(color = "#595959"),
        axis.line.x = element_line(color = "#595959"),
        axis.line.y = element_line(color = "#595959"),
        legend.position = "none")

fb_bar_data <- binned_data %>%
  group_by(age_group, condition) %>%
  summarise(percent_fb = mean(mean_fb), n = n())

fb_plot <- ggplot(binned_data, aes(x = as.numeric(factor(age_group)), y = mean_fb)) +
  geom_col(data = fb_bar_data, aes(x = age_group, y = percent_fb, fill = condition),
           position = "dodge", alpha = 0.3) +
  geom_smooth(method = "glm", method.args = list(family = "quasibinomial"),
              formula = y ~ x + I(x^2), aes(color = condition)) +
  scale_y_continuous(limits = c(0, 1), breaks = c(0, 0.2, 0.4, 0.6, 0.8, 1)) +
  scale_fill_manual(values = c("#999999", "#3D2785")) +
  scale_color_manual(values = c("#999999", "#3D2785")) +
  labs(title = "Standard False Belief Task",
       x = "Age",
       y = "Average False Belief Score",
       color = "Condition") +
  guides(color = guide_legend(order = 1),
         fill = "none") +
  theme(plot.title = element_text(size = 18, color = "#595959", family = "Avenir Heavy"),
        text = element_text(size = 14, color = "#595959", family = "Avenir Medium"),
        axis.text = element_text(size = 12, color = "#595959", family = "Avenir Medium"),
        axis.ticks = element_line(color = "#595959"),
        axis.line.x = element_line(color = "#595959"),
        axis.line.y = element_line(color = "#595959"),
        legend.position = "none")

# Extract legend from a temporary plot
legend_plot <- key_plot +
  theme(legend.position = "bottom",
        legend.text = element_text(size = 12, color = "#595959", family = "Avenir Medium"),
        legend.title = element_text(face = "bold", color = "#595959"))
shared_legend <- get_legend(legend_plot)

# Combine plots with legend below
fig3 <- grid.arrange(
  arrangeGrob(key_plot, fb_plot, ncol = 2),
  shared_legend,
  nrow = 2,
  heights = c(10, 1)
)

# Export
ggsave("fig3.png", plot = fig3, width = 10, height = 5, dpi = 300)
```


## Effect of Smart Speaker Experience in AI Condition (age > peak of inv-U curve to focus on the declining trend)
```{r ss_experience}

# main analysis: looking at heavy smart speaker users vs non-heavy users: children who have 2+ smart speakers at home AND use them daily

heavySS <- data_e2 %>%
  filter(condition == "AI" & age >= peak_age) %>%  
  mutate(heavy_ss_user = (num_speakers >= 2) & (ss_daily == TRUE)) %>%
  filter(!is.na(heavy_ss_user))

heavySS %>%
  group_by(heavy_ss_user) %>%
  summarise(n = n(), mean_age = mean(age), sd_age = sd(age))

mod_heavySS <- glm(chose_song_1 ~ age + heavy_ss_user, family = binomial, data = heavySS)
summary(mod_heavySS)
nobs(mod_heavySS)

```


```{r ss_followup analyses}

# follow-up 1: looking at daily smart speaker usage
mod_daily <- glm(chose_song_1 ~ age + ss_daily, family = binomial, data = heavySS)
summary(mod_daily)
nobs(mod_daily)


# follow-up 2: looking at number of speakers 
mod_numss <- glm(chose_song_1 ~ age + num_speakers, family = binomial, data = heavySS)
summary(mod_numss)
nobs(mod_numss)
```


## Heavy Smart Speaker Users by Age Group (AI condition, ages 7+)
```{r plot_SS}
# heavy_ss_user: owns 2+ smart speakers AND uses daily (same as the above analysis)
# age bins: 7-8, 9-10, 11-12, 13+ (instead of plotting from peak_age, use binned age groups, starting from 7 yr olds)



heavySS_over7 <- data_e2 %>%
  filter(condition == "AI" & age >= 7 & !is.na(num_speakers) & !is.na(ss_daily)) %>%
  mutate(
    heavy_ss_user = (num_speakers >= 2) & (ss_daily == TRUE),
    heavy_ss_user = ifelse(heavy_ss_user, "Heavy SS user", "Not heavy SS user"),
    age_bin = case_when(
      age < 9  ~ "7-8",
      age < 11 ~ "9-10",
      age < 13 ~ "11-12",
      TRUE     ~ "13+"
    ),
    age_bin = factor(age_bin, levels = c("7-8", "9-10", "11-12", "13+"))
  )


heavySS_bar_over7 <- heavySS_over7 %>%
  group_by(age_bin, heavy_ss_user) %>%
  summarise(percent_song_1 = mean(chose_song_1), n = n(), .groups = "drop")

ggplot(heavySS_bar_over7, aes(x = age_bin, y = percent_song_1, fill = heavy_ss_user)) +
  geom_col(position = "dodge") +
  geom_text(aes(label = paste0("n=", n)),
            position = position_dodge(width = 0.9),
            vjust = -0.5, size = 3, color = "#595959") +
  scale_y_continuous(limits = c(0, 1.15), breaks = c(0, 0.2, 0.4, 0.6, 0.8, 1)) +
  scale_fill_manual(values = c("Heavy SS user" = "#3D2785", "Not heavy SS user" = "#B6A6E9")) +
  labs(title = "Impact of Heavy Smart Speaker Use",
       x = "Age",
       y = "Percent Consistent w/ Separate Minds",
       fill = "Smart Speaker\nExperience") +
  theme(plot.title = element_text(size = 18, color = "#595959", family = "Avenir Heavy"),
        text = element_text(size = 14, color = "#595959", family = "Avenir Medium"),
        axis.text = element_text(size = 12, color = "#595959", family = "Avenir Medium"),
        axis.ticks = element_line(color = "#595959"),
        axis.line.x = element_line(color = "#595959"),
        axis.line.y = element_line(color = "#595959"),
        legend.position = "right",
        legend.justification = "left",
        legend.text = element_text(size = 12),
        legend.title = element_text(face = "bold"))

ggsave("fig4.png", width = 8, height = 5, dpi = 300)

```



## Daily Smart Speaker Usage by Age Group (AI condition, ages 7+)
```{r plot_dailySS}
dailySS_data <- data_e2 %>%
  filter(condition == "AI" & age >= 7 & !is.na(ss_daily)) %>%
  mutate(
    ss_daily_label = ifelse(ss_daily, "Daily", "Less than Daily"),
    age_bin = case_when(
      age < 9  ~ "7-8",
      age < 11 ~ "9-10",
      age < 13 ~ "11-12",
      TRUE     ~ "13+"
    ),
    age_bin = factor(age_bin, levels = c("7-8", "9-10", "11-12", "13+"))
  )

dailySS_bar_data <- dailySS_data %>%
  group_by(age_bin, ss_daily_label) %>%
  summarise(percent_song_1 = mean(chose_song_1), n = n(), .groups = "drop")

ggplot(dailySS_bar_data, aes(x = age_bin, y = percent_song_1, fill = ss_daily_label)) +
  geom_col(position = "dodge") +
  geom_text(aes(label = paste0("n=", n)),
            position = position_dodge(width = 0.9),
            vjust = -0.5, size = 3, color = "#595959") +
  scale_y_continuous(limits = c(0, 1.15), breaks = c(0, 0.2, 0.4, 0.6, 0.8, 1)) +
  scale_fill_manual(values = c("Daily" = "#3D2785", "Less than Daily" = "#B6A6E9")) +
  labs(title = "Impact of Daily Smart Speaker Usage",
       x = "Age",
       y = "Percent Consistent w/ Separate Minds",
       fill = "Smart Speaker\nUsage Frequency") +
  theme(plot.title = element_text(size = 18, color = "#595959", family = "Avenir Heavy"),
        text = element_text(size = 14, color = "#595959", family = "Avenir Medium"),
        axis.text = element_text(size = 12, color = "#595959", family = "Avenir Medium"),
        axis.ticks = element_line(color = "#595959"),
        axis.line.x = element_line(color = "#595959"),
        axis.line.y = element_line(color = "#595959"),
        legend.position = "right",
        legend.justification = "left",
        legend.text = element_text(size = 12),
        legend.title = element_text(face = "bold"))
```



