---
title: "Experiment 2"
output: pdf_document
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)
```

# Setup
```{r libraries}
library(tidyverse)
library(readxl)
library(irr)
theme_set(theme_classic())
```

# Read Data
```{r read_data}
data_e2 <- read_csv("Experiment2_data.csv")
```

# Demographics
```{r demographics}
# Age
data_e2 %>% summarise(
  mean_age = mean(age),
  sd_age = sd(age),
  n = n())

# Condition
data_e2 %>%
  group_by(condition) %>%
  summarize(condition_count = n())

# Gender
data_e2 %>%
  count(child_gender)
```

# Preregistered Analyses

## Exploratory: Relationship between ToM and Person condition
```{r tom_person}
mod_tom <- data_e2 %>%
  filter(condition == "Person") %>%
  glm(chose_song_1 ~ mean_fb, family = binomial, data = .)

summary(mod_tom)
```

## H1: Effect of Age by Condition
```{r h1_age_condition}
mod_h1 <- glm(chose_song_1 ~ 1 + age * condition, family = binomial, data_e2)
summary(mod_h1)
```

## H2: Quadratic Regression in AI Condition
```{r h2_quadratic_ai}
data_ai <- data_e2 %>%
  filter(condition == "AI") %>%
  mutate(age_c  = age - mean(age),
         age_c2 = age_c^2)

mod_h2 <- glm(chose_song_1 ~ age_c + age_c2, family = binomial, data_ai)
summary(mod_h2)
```

# Exploratory Analyses

## Quadratic Regression in Person Condition
```{r quadratic_person}
data_person <- data_e2 %>%
  filter(condition == "Person") %>%
  mutate(age_c  = age - mean(age),
         age_c2 = age_c^2)

mod_quadratic_person <- glm(chose_song_1 ~ age_c + age_c2, family = binomial, data_person)
summary(mod_quadratic_person)
```

## Full Model: Interaction of Quadratic Age and Condition
```{r full_model}
# Center age on the overall mean for the full model
data_e2 <- data_e2 %>%
  mutate(age_c  = age - mean(age),
         age_c2 = age_c^2)

mod_full <- glm(chose_song_1 ~ (age_c + age_c2) * condition, family = binomial, data_e2)
summary(mod_full)
```

## Main Task and False Belief by Age
```{r plot_age}
require(gridExtra)

binned_data <- data_e2
binned_data$age_group <- cut(data_e2$age,
                             breaks = c(3, 5, 7, 9, 11, 13, Inf),
                             labels = c("3-4", "5-6", "7-8", "9-10", "11-12", "13+"),
                             right = FALSE)

binned_data <- binned_data %>%
  mutate(condition = factor(condition, levels = c("Person", "AI")))

bar_data <- binned_data %>%
  group_by(age_group, condition) %>%
  summarise(percent_song_1 = mean(chose_song_1),
            n = n())

key_plot <- ggplot(binned_data, aes(x = as.numeric(factor(age_group)), y = chose_song_1)) +
  geom_col(data = bar_data, aes(x = age_group, y = percent_song_1, fill = condition),
           position = "Dodge", alpha = 0.3) +
  geom_smooth(method = "glm", method.args = list(family = "binomial"),
              formula = y ~ x + I(x^2), aes(color = condition)) +
  scale_y_continuous(limits = c(0, 1), breaks = c(0, 0.2, 0.4, 0.6, 0.8, 1)) +
  scale_fill_manual(values = c("#999999", "#3D2785")) +
  scale_color_manual(values = c("#999999", "#3D2785")) +
  labs(title = "Main Task",
       x = "Age",
       y = "Percent Consistent w/ Separate Minds",
       color = "Condition") +
  guides(color = guide_legend(order = 1),
         linetype = guide_legend(order = 2),
         fill = "none") +
  theme(plot.title = element_text(size = 18, color = "#595959", family = "Avenir Heavy"),
        text = element_text(size = 14, color = "#595959", family = "Avenir Medium"),
        axis.text = element_text(size = 12, color = "#595959", family = "Avenir Medium"),
        axis.ticks = element_line(color = "#595959"),
        axis.line.x = element_line(color = "#595959"),
        axis.line.y = element_line(color = "#595959"),
        legend.position = "none",
        legend.justification = "left",
        legend.text = element_text(size = 12),
        legend.title = element_text(face = "bold"))

key_plot

fb_bar_data <- binned_data %>%
  group_by(age_group, condition) %>%
  summarise(percent_fb = mean(mean_fb),
            n = n())

fb_plot <- ggplot(binned_data, aes(x = as.numeric(factor(age_group)), y = mean_fb)) +
  geom_col(data = fb_bar_data, aes(x = age_group, y = percent_fb, fill = condition),
           position = "Dodge", alpha = 0.3) +
  geom_smooth(method = "glm", method.args = list(family = "binomial"),
              formula = y ~ x, aes(color = condition)) +
  scale_y_continuous(limits = c(0, 1), breaks = c(0, 0.2, 0.4, 0.6, 0.8, 1)) +
  scale_fill_manual(values = c("#999999", "#3D2785")) +
  scale_color_manual(values = c("#999999", "#3D2785")) +
  labs(title = "Standard False Belief Task",
       x = "Age",
       y = "Average False Belief Score",
       color = "Condition") +
  guides(color = guide_legend(order = 1),
         linetype = guide_legend(order = 2),
         fill = "none") +
  theme(plot.title = element_text(size = 18, color = "#595959", family = "Avenir Heavy"),
        text = element_text(size = 14, color = "#595959", family = "Avenir Medium"),
        axis.text = element_text(size = 12, color = "#595959", family = "Avenir Medium"),
        axis.ticks = element_line(color = "#595959"),
        axis.line.x = element_line(color = "#595959"),
        axis.line.y = element_line(color = "#595959"),
        legend.position = "none",
        legend.justification = "left",
        legend.text = element_text(size = 12),
        legend.title = element_text(face = "bold"))

fb_plot

grid.arrange(key_plot, fb_plot, ncol = 2)
```


## Effect of Smart Speaker Experience in AI Condition (age > 9)
```{r ss_experience}
# Restrict analysis to children aged 9 and up
data_ai_decline <- data_ai %>%
  filter(age > 9)

# Multiple smart speaker ownership (2 or more) — reported in paper
mod_multi <- glm(chose_song_1 ~ age_c + multiSSexperience, family = binomial, data = data_ai_decline)
summary(mod_multi)

# Daily smart speaker usage
mod_daily <- glm(chose_song_1 ~ age_c + ss_daily, family = binomial, data = data_ai_decline)
summary(mod_daily)


```

# Plots

## Smart Speaker Ownership by Age Group (AI condition, age > 9)
```{r plot_multiSS}
multiSS_data <- data_e2 %>%
  filter(condition == "AI" & age > 9 & !is.na(multiSSexperience)) %>%
  mutate(
    age_bin = case_when(
      floor(age) <= 10 ~ "9-10",
      floor(age) <= 12 ~ "11-12",
      TRUE             ~ "13-15"
    ),
    age_bin = factor(age_bin, levels = c("9-10", "11-12", "13-15")),
    multiSSexperience = ifelse(multiSSexperience, "2 or more", "Less than 2")
  )

multiSS_bar_data <- multiSS_data %>%
  group_by(age_bin, multiSSexperience) %>%
  summarise(percent_song_1 = mean(chose_song_1), n = n(), .groups = "drop")

ggplot(multiSS_bar_data, aes(x = age_bin, y = percent_song_1, fill = multiSSexperience)) +
  geom_col(position = "dodge") +
  geom_text(aes(label = paste0("n=", n)),
            position = position_dodge(width = 0.9),
            vjust = -0.5, size = 3, color = "#595959") +
  scale_y_continuous(limits = c(0, 1.15), breaks = c(0, 0.2, 0.4, 0.6, 0.8, 1)) +
  scale_fill_manual(values = c("2 or more" = "#3D2785", "Less than 2" = "#B6A6E9")) +
  labs(title = "Impact of Owning Multiple Smart Speakers",
       x = "Age",
       y = "Percent Consistent w/ Separate Minds",
       fill = "Number of Smart\nSpeakers in Home") +
  theme(plot.title = element_text(size = 18, color = "#595959", family = "Avenir Heavy"),
        text = element_text(size = 14, color = "#595959", family = "Avenir Medium"),
        axis.text = element_text(size = 12, color = "#595959", family = "Avenir Medium"),
        axis.ticks = element_line(color = "#595959"),
        axis.line.x = element_line(color = "#595959"),
        axis.line.y = element_line(color = "#595959"),
        legend.position = "right",
        legend.justification = "left",
        legend.text = element_text(size = 12),
        legend.title = element_text(face = "bold"))
  nrow(multiSS_data)
```

## Daily Smart Speaker Usage by Age Group (AI condition, age > 9)
```{r plot_dailySS}
dailySS_data <- data_e2 %>%
  filter(condition == "AI" & age > 9 & !is.na(ss_daily)) %>%
  mutate(
    age_bin = case_when(
      floor(age) <= 10 ~ "9-10",
      floor(age) <= 12 ~ "11-12",
      TRUE             ~ "13-15"
    ),
    age_bin = factor(age_bin, levels = c("9-10", "11-12", "13-15")),
    ss_daily = ifelse(ss_daily, "Daily", "Less than Daily")
  )

dailySS_bar_data <- dailySS_data %>%
  group_by(age_bin, ss_daily) %>%
  summarise(percent_song_1 = mean(chose_song_1), n = n(), .groups = "drop")

ggplot(dailySS_bar_data, aes(x = age_bin, y = percent_song_1, fill = ss_daily)) +
  geom_col(position = "dodge") +
  geom_text(aes(label = paste0("n=", n)),
            position = position_dodge(width = 0.9),
            vjust = -0.5, size = 3, color = "#595959") +
  scale_y_continuous(limits = c(0, 1.15), breaks = c(0, 0.2, 0.4, 0.6, 0.8, 1)) +
  scale_fill_manual(values = c("Daily" = "#3D2785", "Less than Daily" = "#B6A6E9")) +
  labs(title = "Impact of Daily Smart Speaker Usage",
       x = "Age",
       y = "Percent Consistent w/ Separate Minds",
       fill = "Smart Speaker\nUsage Frequency") +
  theme(plot.title = element_text(size = 18, color = "#595959", family = "Avenir Heavy"),
        text = element_text(size = 14, color = "#595959", family = "Avenir Medium"),
        axis.text = element_text(size = 12, color = "#595959", family = "Avenir Medium"),
        axis.ticks = element_line(color = "#595959"),
        axis.line.x = element_line(color = "#595959"),
        axis.line.y = element_line(color = "#595959"),
        legend.position = "right",
        legend.justification = "left",
        legend.text = element_text(face = "bold"))
  nrow(dailySS_data)
```

