---
title: "LookIt Analysis"
output: pdf_document
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)
```

# Setup
```{r setup}
library(tidyverse)
library(readxl)
library(irr)
theme_set(theme_classic())

se <- function(x, n) {
  sd(x)/sqrt(n)
}

```

# Read Data
```{r data}
data <- read_csv("Experiment2_data.csv")

```

# Demographics
```{r demo}
#Age
data %>% summarise(
  mean_age = mean(age),
  sd_age = sd(age),
  n = n())

#Condition
data %>%
  group_by(condition) %>% 
  summarize(
    condition_count = n())

#Gender
data %>% 
  count(child_gender)
  
```

# Preregistered Analyses

## Exploratory: Relationship between ToM and Person condition
```{r}
model_tom <- data %>%
  filter(condition == "Person") %>%
  glm(chose_song_1 ~ mean_fb, family = binomial, data = .)

summary(model_tom)

```

## H1: Effect of Age by Condition
```{r h1}
mod <- glm(chose_song_1 ~ 1 + age * condition, family = binomial, data)
summary(mod)

```

## H2: Quadratic Regression in AI condition
```{r h1}
data_AI <- data %>% 
  filter(condition == "AI") %>% 
  mutate(age_c = age - mean(age),
         age_c2 = age_c^2)

mod_quadratic_ai <- glm(chose_song_1 ~ age_c + age_c2, family = binomial, data_AI)
summary(mod_quadratic_ai)

```

# Exploratory Analyses

## Quadratic Regression in Person condition
```{r}
data_person <- data %>% 
  filter(condition == "Person") %>% 
  mutate(age_c = age - mean(age),
         age_c2 = age_c^2)

mod_quadratic_person <- glm(chose_song_1 ~ age_c + age_c2, family = binomial, data_person)
summary(mod_quadratic_person)

```

## Full Model: Interaction of Quadratic Age and Condition
```{r}
data <- data %>% 
  mutate(age_c = age - mean(age),
         age_c2 = age_c^2)

mod_full <- glm(chose_song_1 ~ (age_c + age_c2) * condition, family = binomial, data)
summary(mod_full)

```

# Effect of Smart Speaker Experience in AI condition beyond age 9
```{r}
df_ai_decline <- data_AI %>%
  filter(age > 9)  

m_daily <- glm(chose_song_1 ~ age_c + ss_daily, family = binomial, data = df_ai_decline)
m_multi <- glm(chose_song_1 ~ age_c + multiSSexperience , family = binomial, data = df_ai_decline) #this is what we're reporting

summary(m_daily)
summary(m_multi)

```

## Plot Age
```{r data}
require(gridExtra)
binned_data <- data
binned_data$age_group <- cut(data$age,
                    breaks = c(3, 5, 7, 9, 11, 13, Inf),
                    labels = c("3-4", "5-6", "7-8", "9-10", "11-12", "13+"),
                    right = FALSE)

binned_data <- binned_data %>% 
  mutate(condition = factor(condition, levels = c("Person", "AI")))  

bar_data <- binned_data %>% 
  group_by(age_group, condition) %>% 
  summarise(percent_song_1 = mean(chose_song_1),
            n = n())

key_plot <- ggplot(binned_data, aes(x=as.numeric(factor(age_group)), y=chose_song_1)) +
  geom_col(data=bar_data, aes(x=age_group, y=percent_song_1, fill=condition), position="Dodge", alpha=0.3) +
  geom_smooth(method = "glm", method.args = list(family = "binomial"), formula = y ~ x + I(x^2), aes(color=condition)) +
  scale_y_continuous(limits=c(0,1),breaks=c(0,0.2,0.4,0.6,0.8,1)) +
  scale_fill_manual(values=c("#999999", "#3D2785")) +
  scale_color_manual(values=c( "#999999", "#3D2785")) +
  labs(title = "Main Task",
       x = "Age",
       y = "Percent Consistent w/ Separate Minds",
       color = "Condition") +
  guides(color = guide_legend(order = 1), 
        linetype = guide_legend(order = 2),
        fill = "none") +
  theme(plot.title = element_text(size = 18, color = "#595959", family = "Avenir Heavy"),
        text = element_text(size = 14, color = "#595959", family = "Avenir Medium"),
        axis.text = element_text(size = 12, color = "#595959", family = "Avenir Medium"),
        axis.ticks = element_line(color = "#595959"),
        axis.line.x = element_line(color = "#595959"),
        axis.line.y = element_line(color = "#595959"),
        legend.position = "none",
        legend.justification = "left",
        legend.text = element_text(size = 12),
        legend.title = element_text(face = "bold"))

key_plot

fb_bar_data <- binned_data %>% 
  group_by(age_group, condition) %>% 
  summarise(percent_fb = mean(mean_fb),
            n = n())

fb_plot <- ggplot(binned_data, aes(x=as.numeric(factor(age_group)), y=mean_fb)) +
  geom_col(data=fb_bar_data, aes(x=age_group, y=percent_fb, fill=condition), position="Dodge", alpha=0.3) +
  geom_smooth(method = "glm", method.args = list(family = "binomial"), formula = y ~ x, aes(color=condition)) +
  # geom_smooth(method = "lm", formula = y ~ x, aes(color=condition)) +
  scale_y_continuous(limits=c(0,1),breaks=c(0,0.2,0.4,0.6,0.8,1)) +
  scale_fill_manual(values=c("#999999", "#3D2785")) +
  scale_color_manual(values=c("#999999", "#3D2785")) +
  labs(title = "Standard False Belief Task",
       x = "Age",
       y = "Average False Belief Score",
       color = "Condition") +
  guides(color = guide_legend(order = 1), 
        linetype = guide_legend(order = 2),
        fill = "none") +
  theme(plot.title = element_text(size = 18, color = "#595959", family = "Avenir Heavy"),
        text = element_text(size = 14, color = "#595959", family = "Avenir Medium"),
        axis.text = element_text(size = 12, color = "#595959", family = "Avenir Medium"),
        axis.ticks = element_line(color = "#595959"),
        axis.line.x = element_line(color = "#595959"),
        axis.line.y = element_line(color = "#595959"),
        legend.position = "none",
        legend.justification = "left",
        legend.text = element_text(size = 12),
        legend.title = element_text(face = "bold"))

fb_plot 

grid.arrange(key_plot, fb_plot, ncol=2)

```


## Exploratory
```{r exploratory_multiSS}
multiSS_data <- data %>% filter(condition=="AI" & !is.na(multiSSexperience))
mod <- glm(chose_song_1 ~ 1 + age^2 * multiSSexperience, family = binomial, multiSS_data)
summary(mod)

multiSS_data$age_group <- cut(multiSS_data$age,
                    breaks = c(3, 5, 7, 9, 11, 13, Inf),
                    labels = c("3-4", "5-6", "7-8", "9-10", "11-12", "13+"),
                    right = FALSE)

multiSS_data$multiSSexperience[multiSS_data$multiSSexperience == TRUE] <- "2 or more"
multiSS_data$multiSSexperience[multiSS_data$multiSSexperience == FALSE] <- "Less than 2"

multiSS_bar_data <- multiSS_data %>% 
  group_by(age_group, multiSSexperience) %>% 
  summarise(percent_song_1 = mean(chose_song_1),
            n = n())

ggplot(multiSS_data, aes(x=as.numeric(factor(age_group)), y=chose_song_1)) +
  geom_col(data=multiSS_bar_data, aes(x=age_group, y=percent_song_1, fill=multiSSexperience), position="Dodge") +
  scale_y_continuous(limits=c(0,1),breaks=c(0,0.2,0.4,0.6,0.8,1)) +
  scale_fill_manual(values=c("#3D2785", "#B6A6E9")) +
  labs(title = "Impact of Owning Multiple Smart Speakers",
       x = "Age",
       y = "Percent Consistent w/ Separate Minds",
       fill = "Number of Smart\nSeakers in Home") +
  theme(plot.title = element_text(size = 18, color = "#595959", family = "Avenir Heavy"),
        text = element_text(size = 14, color = "#595959", family = "Avenir Medium"),
        axis.text = element_text(size = 12, color = "#595959", family = "Avenir Medium"),
        axis.ticks = element_line(color = "#595959"),
        axis.line.x = element_line(color = "#595959"),
        axis.line.y = element_line(color = "#595959"),
        legend.position = "right",
        legend.justification = "left",
        legend.text = element_text(size = 12),
        legend.title = element_text(face = "bold"))


wide_multiSS <- multiSS_bar_data %>% 
  select(-percent_song_1) %>% 
  pivot_wider(names_from = multiSSexperience, values_from = n)



```



```{r exploratory_dailySS}
exploratory_data <- data %>% filter(condition=="AI" & !is.na(ss_daily))
# exploratory_data <- exploratory_data %>% filter(floor_age >= 6)
mod <- glm(chose_song_1 ~ 1 + age^2 * ss_daily, family = binomial, exploratory_data)
summary(mod)

exploratory_data$age_group <- cut(exploratory_data$age,
                    breaks = c(3, 5, 7, 9, 11, 13, Inf),
                    labels = c("3-4", "5-6", "7-8", "9-10", "11-12", "13+"),
                    right = FALSE)

exploratory_data$ss_daily[exploratory_data$ss_daily == TRUE] <- "Daily"
exploratory_data$ss_daily[exploratory_data$ss_daily == FALSE] <- "Less than Daily"

exploratory_bar_data <- exploratory_data %>% 
  group_by(age_group, ss_daily) %>% 
  summarise(percent_song_1 = mean(chose_song_1),
            n = n())

ggplot(data=exploratory_bar_data %>% filter(age > 9), aes(x=age_group, y=percent_song_1, fill=ss_daily)) +
  geom_col(position="Dodge") +
  scale_y_continuous(limits=c(0,1),breaks=c(0,0.2,0.4,0.6,0.8,1)) +
  scale_fill_manual(values=c("#3D2785", "#B6A6E9")) +
  labs(title = "Impact of Daily Smart Speaker Usage",
       x = "Age",
       y = "Percent Consistent w/ Separate Minds",
       fill = "Smart Speaker\nUsage Frequency") +
  theme(plot.title = element_text(size = 18, color = "#595959", family = "Avenir Heavy"),
        text = element_text(size = 14, color = "#595959", family = "Avenir Medium"),
        axis.text = element_text(size = 12, color = "#595959", family = "Avenir Medium"),
        axis.ticks = element_line(color = "#595959"),
        axis.line.x = element_line(color = "#595959"),
        axis.line.y = element_line(color = "#595959"),
        legend.position = "right",
        legend.justification = "left",
        legend.text = element_text(size = 12),
        legend.title = element_text(face = "bold"))


wide_dailySS <- exploratory_bar_data %>% 
  select(-percent_song_1) %>% 
  pivot_wider(names_from = ss_daily, values_from = n)

#===points
exploratory_data_point <- exploratory_data %>% 
  filter(age > 9.14) %>% 
  mutate(age_floor = floor(age)) %>% 
  mutate(ss_daily = as.factor(ss_daily))

## plotting points
ggplot(exploratory_data_point, aes(x=age_floor, y=chose_song_1)) +
  # geom_point(aes(color = ss_daily)) +
  # geom_jitter(aes(color = ss_daily), height = .05, width = .05) +
  geom_smooth(method = "lm", aes(color = ss_daily)) +
  geom_col(aes(x=age_group, y=percent_song_1, fill=multiSSexperience), position="Dodge") +
  scale_y_continuous(limits=c(0,1),breaks=c(0,0.2,0.4,0.6,0.8,1)) +
  scale_color_manual(values=c("#3D2785", "#B6A6E9")) +
  labs(title = "Impact of Owning Multiple Smart Speakers",
       x = "Age",
       y = "Percent Consistent w/ Separate Minds",
       fill = "Number of Smart\nSeakers in Home") +
  theme(plot.title = element_text(size = 18, color = "#595959", family = "Avenir Heavy"),
        text = element_text(size = 14, color = "#595959", family = "Avenir Medium"),
        axis.text = element_text(size = 12, color = "#595959", family = "Avenir Medium"),
        axis.ticks = element_line(color = "#595959"),
        axis.line.x = element_line(color = "#595959"),
        axis.line.y = element_line(color = "#595959"),
        legend.position = "right",
        legend.justification = "left",
        legend.text = element_text(size = 12),
        legend.title = element_text(face = "bold"))
```
