---
title: "Experiment2_Preprocessing"
output: html_document
date: "2026-06-09"
---

README

This script adds a gender column to the original data file (i.e. Experiment2_data_original.csv (renamed from Experiment2_data.csv)). It takes as input (1) data.csv (a file generated from running the python script on session data from Lookit), data_with_gender.csv (a file downloaded from Lookit with demographic information), and Experiment2_data_original.csv (the data file we had on the repo originally, which Griffin previously added, and which did not have a gender field). This is because data.csv has the child_ids used to identify unique children, and data_with_gender.csv has the gender information. It creates the output file: Experiment2_data.csv.

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)
```

## Setup
```{r setup}
library(tidyverse)
library(readxl)
library(irr)
theme_set(theme_classic())

```

## Import data

```{r}
#raw session data (that was on script, that seems to have been wrangled post-Lookit export but we don't know how exactly)
data <- read_csv("Experiment2_data_original.csv")

#raw session data directly from lookit
data_lookit <- read_csv("data.csv") %>% 
  rename("child_id" = child__hashed_id) %>% 
  mutate(condition = ifelse(condition == "person", "Person", condition))

#demographic data from lookit
dat_gender <- read_csv("data_with_gender.csv") 

```

# Append Gender
```{r}
#Join and count
columns_to_join <- c("condition", "counterbalance", "attn1", "attn2", "attn3", "test", 
               "rachel_false_belief", "diana_false_belief", "allie_false_belief", 
               "num_speakers", "coding_experience", "smartphone_frequency", 
               "smart_speaker_frequency", "voice_assistant_frequency", "pass_attn1", 
               "pass_attn2", "pass_attn3", "pass_all_attn", "chose_song_1")

sessions_indexed <- data %>%
  group_by(across(all_of(columns_to_join))) %>%
  mutate(match_num = row_number()) %>%
  ungroup()

# raw_indexed <- data %>%
raw_indexed <- data_lookit %>%
  filter(!(child_id == "YM2G5C" & counterbalance == 0)) %>%
  group_by(across(all_of(columns_to_join))) %>%
  mutate(match_num = row_number()) %>%
  ungroup() %>%
  select(child_id, all_of(columns_to_join), match_num)

data_sessions_with_ids <- sessions_indexed %>%
  left_join(
    raw_indexed,
    # by = c(join_cols, "match_num")) %>%
    by = c(columns_to_join, "match_num")) %>%
  select(-match_num) %>% 
  relocate(child_id, .before = age_days)

#add gender
gender_lookup <- dat_gender %>%
  distinct(child_id, .keep_all = TRUE) %>%
  select(child_id, child_age_rounded, child_gender)

data_sessions_with_gender <- data_sessions_with_ids %>%
  left_join(gender_lookup, by = "child_id") %>% 
  relocate(child_gender, .after = child_id) %>% 
  relocate(child_age_rounded, .after = child_gender)

data <- data_sessions_with_gender %>% 
  mutate(age = age_days/365.25,
         age_months = age_days/30.417,
         floor_age = floor(age)) %>% 
  rowwise() %>% 
  mutate(mean_fb = sum(rachel_false_belief, diana_false_belief, allie_false_belief) / 3) %>% 
  relocate(age, .after = age_days) %>% 
  relocate(mean_fb, .after = allie_false_belief)

data$voice_assistant_frequency = factor(data$voice_assistant_frequency, levels = c("Never", "Less than once a week
", "About once a week", "About once a day", "Several times a day"))
data <- data %>% mutate(va_daily = (voice_assistant_frequency == "About once a day" | voice_assistant_frequency == "Several times a day"))
data <- data %>% mutate(ss_daily = (smart_speaker_frequency == "About once a day" | smart_speaker_frequency == "Several times a day"))
data <- data %>% mutate(multiSSexperience = (num_speakers >= 2))

data

```


# Export
```{r}
write.csv(data, "Experiment2_data.csv", row.names = FALSE)
```





