---
title: "Zoom Pilot Analysis (SI)"
output: pdf_document
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)
```

# Setup
```{r libraries}
library(tidyverse)
library(readxl)
library(irr)
theme_set(theme_classic())

se <- function(x, n) {
  sd(x)/sqrt(n)
}
```

# Read Data
```{r read_data}
si_data <- read_csv("SI_data.csv") %>%
  filter(usable == 1 &
           english_all_or_most_or_first_lang_or_school == 1) %>%
  mutate(
    chose_song_1     = ifelse(first_song == test_q, 1, 0),
    multiSSexperience = as.integer(number_of_SS_in_home) > 1,
    mean_fb         = (rachel_prediction_implicit_false_belief +
                          diana_prediction_false_belief_location +
                          allie_predicition_false_belief_location) / 3.0,
    fb_over_2        = as.integer(
                         (rachel_prediction_implicit_false_belief +
                            diana_prediction_false_belief_location +
                            allie_predicition_false_belief_location) >= 2)
  )

# Recode VUI → AI and set factor levels
si_data$condition <- recode(si_data$condition, "VUI" = "AI")
si_data$condition <- factor(si_data$condition, levels = c("Person", "AI"))

```

# Demographics
```{r demographics}
# Age
si_data %>% summarise(
  mean_age = mean(age),
  sd_age   = sd(age),
  n        = n())

# Condition
si_data %>%
  group_by(condition) %>%
  summarize(condition_count = n())

# Gender
si_data %>%
  count(gender)
```

# Preregistered Analyses

## Exploratory: Relationship between False Belief Score and Person Condition
```{r tom_person}
# mean_fb: mean of 3 standard false belief trials 
mod_tom <- si_data %>%
  filter(condition == "Person") %>%
  glm(chose_song_1 ~ mean_fb, family = binomial, data = .)

summary(mod_tom)
```

## H1: Effect of Age by Condition
```{r h1_age_condition}
mod_h1 <- glm(chose_song_1 ~ 1 + age * condition, family = binomial, si_data)
summary(mod_h1)
```

## H2: Quadratic Regression in AI Condition
```{r h2_quadratic_ai}
si_data_ai <- si_data %>%
  filter(condition == "AI") %>%
  mutate(age_c  = age - mean(age),
         age_c2 = age_c^2)

mod_quadratic_ai <- glm(chose_song_1 ~ age_c + age_c2, family = binomial, si_data_ai)
summary(mod_quadratic_ai)
```

# Exploratory Analyses

## Quadratic Regression in Person Condition
```{r quadratic_person}
si_data_person <- si_data %>%
  filter(condition == "Person") %>%
  mutate(age_c  = age - mean(age),
         age_c2 = age_c^2)

mod_quadratic_person <- glm(chose_song_1 ~ age_c + age_c2, family = binomial, si_data_person)
summary(mod_quadratic_person)
```

## Full Model: Interaction of Quadratic Age and Condition
```{r full_model}
# Center age on the overall mean for the full model
si_data <- si_data %>%
  mutate(age_c  = age - mean(age),
         age_c2 = age_c^2)

mod_full <- glm(chose_song_1 ~ (age_c + age_c2) * condition, family = binomial, si_data)
summary(mod_full)
```

## Effect of Smart Speaker Experience in AI Condition (age > 6)
```{r ss_experience}
# 6 is approximately the median age; restricts to the older half
si_data_ai_older <- si_data_ai %>%
  filter(age > 6)

# Any smart speaker ownership (SS_experience: binary 0/1)
mod_ss <- glm(chose_song_1 ~ age_c + SS_experience, family = binomial, data = si_data_ai_older)
summary(mod_ss)

# Multiple smart speaker ownership (2 or more)
mod_multi <- glm(chose_song_1 ~ age_c + multiSSexperience, family = binomial, data = si_data_ai_older)
summary(mod_multi)
```

# Plots

## Main Task and False Belief by Age
```{r plot_age}
require(gridExtra)

binned_si_data <- si_data
binned_si_data$age_group <- cut(si_data$age,
                             breaks = c(3, 5, 7, Inf),
                             labels = c("3-4", "5-6", "7-8"),
                             right = FALSE)

binned_si_data <- binned_si_data %>%
  mutate(condition = factor(condition, levels = c("Person", "AI")))

bar_si_data <- binned_si_data %>%
  group_by(age_group, condition) %>%
  summarise(percent_song_1 = mean(chose_song_1),
            n = n())

key_plot <- ggplot(binned_si_data, aes(x = as.numeric(factor(age_group)), y = chose_song_1)) +
  geom_col(data = bar_si_data, aes(x = age_group, y = percent_song_1, fill = condition),
           position = "Dodge", alpha = 0.3) +
  geom_smooth(method = "glm", method.args = list(family = "binomial"),
              formula = y ~ x + I(x^2), aes(color = condition)) +
  scale_y_continuous(limits = c(0, 1), breaks = c(0, 0.2, 0.4, 0.6, 0.8, 1)) +
  scale_fill_manual(values = c("#999999", "#3D2785")) +
  scale_color_manual(values = c("#999999", "#3D2785")) +
  labs(title = "Main Task",
       x = "Age",
       y = "Percent Consistent w/ Separate Minds",
       color = "Condition") +
  guides(color = guide_legend(order = 1),
         linetype = guide_legend(order = 2),
         fill = "none") +
  theme(plot.title = element_text(size = 18, color = "#595959", family = "Avenir Heavy"),
        text = element_text(size = 14, color = "#595959", family = "Avenir Medium"),
        axis.text = element_text(size = 12, color = "#595959", family = "Avenir Medium"),
        axis.ticks = element_line(color = "#595959"),
        axis.line.x = element_line(color = "#595959"),
        axis.line.y = element_line(color = "#595959"),
        legend.position = "none",
        legend.justification = "left",
        legend.text = element_text(size = 12),
        legend.title = element_text(face = "bold"))

key_plot

fb_bar_si_data <- binned_si_data %>%
  group_by(age_group, condition) %>%
  summarise(percent_fb = mean(mean_fb),
            n = n())

fb_plot <- ggplot(binned_si_data, aes(x = as.numeric(factor(age_group)), y = mean_fb)) +
  geom_col(data = fb_bar_si_data, aes(x = age_group, y = percent_fb, fill = condition),
           position = "Dodge", alpha = 0.3) +
  geom_smooth(method = "glm", method.args = list(family = "binomial"),
              formula = y ~ x, aes(color = condition)) +
  scale_y_continuous(limits = c(0, 1), breaks = c(0, 0.2, 0.4, 0.6, 0.8, 1)) +
  scale_fill_manual(values = c("#999999", "#3D2785")) +
  scale_color_manual(values = c("#999999", "#3D2785")) +
  labs(title = "False Belief Task",
       x = "Age",
       y = "Average False Belief Score",
       color = "Condition") +
  guides(color = guide_legend(order = 1),
         linetype = guide_legend(order = 2),
         fill = "none") +
  theme(plot.title = element_text(size = 18, color = "#595959", family = "Avenir Heavy"),
        text = element_text(size = 14, color = "#595959", family = "Avenir Medium"),
        axis.text = element_text(size = 12, color = "#595959", family = "Avenir Medium"),
        axis.ticks = element_line(color = "#595959"),
        axis.line.x = element_line(color = "#595959"),
        axis.line.y = element_line(color = "#595959"),
        legend.position = "none",
        legend.justification = "left",
        legend.text = element_text(size = 12),
        legend.title = element_text(face = "bold"))

fb_plot

grid.arrange(key_plot, fb_plot, ncol = 2)
```
